
\section{Introduction}
\label{sec:intro}

Improving the latency of blockchain protocols, in the sense of the time it takes
for a transaction to be ``finalised'', as well as their throughput, in the sense
of the number of transactions they can handle per unit of time, are perhaps the
two most crucial open questions in the area of permissionless distributed
ledgers and remain fundamental barriers for their wider adoption in applications
that require large scale and reasonably expedient transaction processing,
cf.~\cite{scaling}. The Bitcoin blockchain protocol, introduced by
Nakamoto~\cite{bitcoin}, provides settlement with probability of error that
drops exponentially in the number of blocks $k$ that accumulate over a
transaction of interest. This has been informally argued in the original white
paper, and further formally demonstrated in~\cite{gkl}, from where it can be
inferred that the total delay in actual time for a transaction to settle is
linear in $k$ in the worst case. These results were subsequently generalised to
the setting of partial synchrony~\cite{PSS16} and variable
difficulty~\cite{DBLP:conf/crypto/GarayKL17}. Interestingly, this latency
``deficiency'' is intrinsic to the blockchain approach (see below), i.e.,
latency's dependency on $k$ is not a side-effect of the security analysis but
rather a characteristic of the underlying protocol and the threat model it
operates in.

Given the above state of affairs, one has to either change the underlying
settlement protocol or devise some other mechanism that, in conjunction with the
blockchain protocol, achieves high throughput and low latency. A number of works
proceeded with the first direction, e.g., hybrid
consensus~\cite{DBLP:conf/wdag/PassS17},
Algorand~\cite{DBLP:journals/corr/Micali16}. A downside of this approach is that
the resulting protocols fundamentally change the threat model within which
Bitcoin is supposed to operate, e.g., by reducing the threshold of corrupted
players, strengthening the underlying cryptographic assumptions or complicating
the setup assumption required (e.g., from a public to a private setup).

The alternative approach is to build an \emph{overlay} protocol that utilises
the blockchain protocol as a ``fall back'' layer and does not relax the threat
model in anyway while it facilitates fast ``off-chain'' settlement under certain
additional assumptions.  We note that in light of the impossibility result
regarding protocol ``responsiveness'' from~\cite{DBLP:conf/wdag/PassS17} that
states that no protocol can provide settlement in time proportional to actual
network delay (i.e., fast settlement) and provide a security threshold over
$1/3$, we know that maintaining Bitcoin's threat model will require some
additional assumption for the overlay protocol to offer fast settlement.

The first instance of this approach and by far the most widely known and
utilised so far, came with the \emph{lightning
network}~\cite{lightning}\footnote{The specification available online is a more
descriptive reference for the inner workings of the protocol, see
\url{https://github.com/lightningnetwork/lightning-rfc/blob/master/02-peer-protocol.md}.
See also the raiden network that implements Lightning over Ethereum,
\url{https://raiden.network}.} that provides an overlay mechanism over the
Bitcoin blockchain that introduces and takes advantage of the concept of a
bilateral payment channel. The latency for a transaction becomes linear to
actual network delay and another factor that equals the number of bilateral
payment channel hops in the path that connects the two end-points of the
transaction. If a payment is confirmed by the implicated parties then it is
guaranteed that, should they wish it, \emph{eventually} the ledger will record
``gross'' settlement transactions that are consistent with the payment.
Deviations from this guarantee are cryptographically feasible but deincentivised
via on-chain penalties. Moreover, note that no record of a specific payment
transaction need ever appear on-chain thus the number of lightning transactions
that can be exchanged can reach the maximum capacity the network allows between
the parties, without being impeded by any restrictions of the underlying
blockchain protocol.

The lightning network has been very influential in the space and spun a number
of follow up research and implementations (see below for references). We note
that the lightning network is not the only option for building an overlay over a
blockchain. See e.g.,~\cite{DBLP:conf/eurocrypt/PassS18} for an alternative
approach focusing on reducing latency, where it is shown that if the assumption
is raised to a security threshold of $3/4$ plus the honesty of an additional
special player, it is possible to obtain optimal latency. Nevertheless, this
approach does not offer the throughput benefits that are intrinsic to the
lightning network.
%TODO: clarify above

Despite the importance of the lightning network for blockchain scalability there
is still no work so far providing a thorough formal security analysis. This is a
dire state of affairs given the fact that the protocol is actually currently
operational\footnote{For current deployment statistics see e.g.,
\url{https://1ml.com/statistics}.} and its complexity makes it difficult to
extract precise statements regarding the level of security it offers.

\noindent \textbf{Our Results.} We present the first, to our knowledge, complete
security analysis of the lightning network, which we carry out in the universal
composition (UC) setting. We model the payment overlay that the lightning
network provides as an ideal functionality and we demonstrate how it can be
implemented in a hybrid world which assumes a global ledger functionality. Our
treatment is general and does not assume any specific implementation for the
underlying ledger functionality. The ``paynet'' functionality that we introduce
abstracts all the salient security features achieved by the lightning network.
We subsequently describe the whole lightning protocol in this setting and we
prove that it realises our paynet functionality under standard cryptographic
assumptions; the security guarantees of the functionality reflect specific
environmental conditions regarding the availability of the honest parties to
poll the status of the network. In more details our results are as follows.

\begin{enumerate}
\item We present the $\fpaynet{}$ functionality which abstracts the syntax and
security properties provided by the lightning network. We describe our
$\fpaynet{}$ assuming a global ledger functionality $\ledger$ as defined
in~\cite{BMTZ17}, and further refined in~\cite{genesis}, which we know that is
realised by the Bitcoin blockchain. Our approach not only captures lightning,
but it is also general as it can be applied to any payment network by finely
tuning the following parts of the functionality: the exact channel opening
message sequence, the details of the on-chain checks performed by \fpaynet, the
negligence time bounds and the penalty in case of a malicious closure being
caught. Using $\fpaynet{}$, parties can open and close channels, forward
payments along channel paths in the network as well as poll its status.
Importantly, the functionality keeps track of all the off-chain and on-chain
balances and ensures that when a channel closes, the on-chain balances are in
line with the off-chain ones. In order to handle realistic adversarial
deviations, $\fpaynet{}$ allows the adversary to choose one of the following
outcomes for each multi-hop payment: (i) let it go through as requested, (ii)
charge it to an adversarial party along the path, (iii) charge it to a
\emph{negligent} honest party along the path. This last outcome is a crucial
security characteristic of the lightning network: honest parties are required to
poll the functionality with a frequency that corresponds to their level of
involvement in the network and the properties of the underlying ledger. If a
party does not poll often enough, $\fpaynet{}$ identifies it as negligent and it
may lose funds.

\item We identify for the first time the exact polling requirements so that
honest parties do not lose funds, as a function of the parameters of $\ledger$.
The polling requirements for each party are two-fold: (i) the first type refers
to monitoring for closures of channels of which the party is a member, and is
specified by the parameter ``$\mathrm{delay}$'' (chosen by the party), (ii) the
second type refers to monitoring for specific events related to receiving and
relaying payments. In detail, let \emph{Alice} be an intermediary of a multi-hop
payment. When the payment starts, she specifies two blockheights $h, h'$. Also,
let $a$ the upper bound to the number of blocks that may be finalised in the
ledger from the time a certain transaction is emitted to the time it becomes
finalised (i.e. it is included in a block in the ``stable'' part of the ledger).
\emph{Alice} should then poll twice while her local view of the chain advances
from blockheight $h$ to blockheight $h' - a$. Moreover, the two pollings should
be separated by a time window so that the chain can grow by at least $a$ blocks.

\item We provide a complete pseudocode description of the lightning network
protocol $\Pi_{\mathrm{LN}}$ and prove that it realises $\fpaynet{}$ in the
Random Oracle model. We identify a number of underlying cryptographic primitives
that have been used in the specification of the lightning network in a
non-black-box fashion and without reference. Interestingly, while most of these
primitives are quite standard (a PRF, a Digital Signature scheme and an Identity
Based Signature scheme), the remaining one is slightly less standard. The
\emph{combined digital signature} -- as we chose to call it -- is a special case
of an asymmetric two-party digital signature primitive (e.g.,
see~\cite{DBLP:conf/ndss/NicolosiKDM03} and references therein) with the
following characteristic: One of the two parties, the shareholder, generates and
stores a share of the signing key. The public key of the combined signature can
be determined non-interactively from public information produced by both
parties. Issuing signatures requires the availability of the share, which is
verifiable given the public information provided by the shareholder. We
formalise the combined digital signature primitive and show that the
construction lying within the lightning specification realises it under standard
cryptographic assumptions. In summary, the realisation of $\fpaynet{}$ is
achieved assuming the security of the underlying primitives, which in turn can
be based on EC-DLOG and the Random Oracle model.

\item We prove that a more idealized ledger functionality, i.e. a ledger with
instant finality, is unrealisable even assuming a synchronous multicast network.
This result supports our decision to use the more realistic ledger functionality
of~\cite{BMTZ17}, since it establishes that if our analysis was based on such a
perfect ledger, it would not be relevant for any real world deployment of a
payment network since such software would -- necessarily -- depend on a
non-perfect ledger. This choice also distinguishes our work compared to previous
attempts~\cite{DBLP:conf/ccs/DziembowskiFH18,Malavolta:2017:CPP:3133956.3134096,sprites,perun}
to formalize payment networks.
\end{enumerate}

\noindent \textbf{Related Work.} A first suggestion for building a
unidirectional payment channel appeared in~\cite{spilman}. Bidirectional payment
channels were developed in~\cite{DBLP:conf/sss/DeckerW15} and of course as part
of the lightning network~\cite{lightning}. Subsequent work on the topic dealt
with either improving payment networks by utilising more expressive blockchains
such as Ethereum~\cite{perun}, hardware assumptions, see
e.g.,~\cite{DBLP:conf/systor/LindNEKPS18}, or extending its functionality beyond
payments, to smart contracts,~\cite{sprites} or finally enhancing their privacy,
see
e.g.,~\cite{Malavolta:2017:CPP:3133956.3134096,DBLP:conf/ccs/0001M17,DBLP:conf/ndss/HeilmanABSG17}.
Additional work looked into developing supporting protocols for the payment
networks such as rebalancing~\cite{DBLP:conf/ccs/KhalilG17} or finding routes in
a decentralised fashion~\cite{flare,spider}. With respect to idealising the
payment network functionality in the UC setting, a number of previous
papers~\cite{DBLP:conf/ccs/DziembowskiFH18,Malavolta:2017:CPP:3133956.3134096,sprites,perun}
presented ideal functionalities abstracting the concept, but they did not prove
that the lightning network realises them. The main advantage of our approach
however here is that, for the first time, we present a payment network
functionality that interoperates with a global ledger functionality for which we
know, in light of the results of~\cite{BMTZ17}, that is realisable by the
Bitcoin blockchain and hence also reflects the actual parameters that can be
enforced by the implementation and the exact participation conditions needed for
security. In contrast, previous
work~\cite{DBLP:conf/ccs/DziembowskiFH18,Malavolta:2017:CPP:3133956.3134096,perun}
utilized ``too idealised'' ledger functionalities for their analysis which offer
instant finality; as we prove in Theorem~\ref{theorem:perfectledger}, a
representative variant of these functionalities
(Fig.~\ref{fig:perfectledger:func}) is unrealisable even under strong network
assumptions (cf. Section~\ref{sec:perfect-ledger}). On the other hand,
in~\cite{sprites} the ledger is not explicitly specified as a functionality, but
only informally described. Several smart contracts are formally defined instead
as UC ITMs, which are the entities with which protocols ultimately interact. The
execution model of these contracts and their interaction with the blockchain is
explained in an intuitive way, but a complete formalization of the ledger is
missing.

\noindent \textbf{Organisation.} In Section~\ref{sec:preliminaries} we present
preliminaries for the model we employ and the relevant cryptographic primitives.
In Section~\ref{sec:ov-ln} we present an overview of the lightning network and
in Section~\ref{sec:ln-figures} a concrete example of an open channel is given,
accompanied by figures of the relevant transactions. Our payment network
functionality is given an overview description in Section~\ref{sec:ov-paynet}.
Our abstraction of the core lightning protocol is provided in
Section~\ref{sec:ov-protocol}. We give more details about the combined digital
signature primitive in Section~\ref{sec:ov-combined-ds}. In
Section~\ref{sec:ov-security-proof} we provide an overview of the security
proof. Finally, in Section~\ref{sec:perfect-ledger} we formalise our claim that
a ledger functionality with instant finality is unrealisable. In the appendix,
we first give more details on the preliminary primitives, specifically in
Sections~\ref{sec:ds},\ref{sec:ibs},\ref{sec:prf} we discuss digital signatures,
identity based signatures and pseudorandom functions. Subsequently in
Section~\ref{appendix:combinedsign} we go into more details about combined
digital signatures. The transaction structure that is assumed to be recognised
by the underlying distributed ledger is discussed in
Section~\ref{appendix:txstructure}. The paynet functionality is presented in
detail in Section~\ref{appendix:payfunc}. An exhaustive list of the data a
channel party needs to keep is shown in Section~\ref{sec:channel-data} and the
complete description of protocol $\Pi_{\mathrm{LN}}$ is presented in
Section~\ref{appendix:protocol}. Further, the ledger functionality is presented
in Section~\ref{appendix:ledger}. Subsequently the security proof of the payment
channels is presented in Section~\ref{appendix:secproof} and finally we prove
our claim on the unrealisability of a perfect ledger in
Section~\ref{sec:perfect-ledger:proof}.
