\section{A ledger with instant finality is unrealisable}
\label{sec:perfect-ledger}
  As already mentioned, previous attempts at formalising payment channels in
  UC~\cite{DBLP:conf/ccs/DziembowskiFH18,perun,Malavolta:2017:CPP:3133956.3134096,sprites}
  assume a variant of a ledger functionality with instant finality. We here
  define a representative variant of this approach \perfectledger{}
  (Fig.~\ref{fig:perfectledger:func}) where all submitted transactions are
  instantly added to the ledger and immediately available to be read by all
  players. Subsequently we argue that, albeit an attractive abstraction, such a
  functionality is unrealisable, even under strong network assumptions, i.e. a
  multicast synchronous network $\FnetworkEd^1$.
  Such a network ensures that messages sent by honest parties will be instantly
  delivered to all other parties; no delays can be introduced by the adversary.
  We refer the reader to Appendix~\ref{appendix:ledger} for the formal
  definition of $\FnetworkEd^1$. The adversary however may choose to send its
  own messages only to specific parties. This allows the adversary to spread
  conflicting information or withhold data from some parties. As we will see,
  this adversarial ability precludes the possibility of the ledger of
  Fig.~\ref{fig:perfectledger:func} to be realised. With regards to models where
  the ledger provides instant finality but the adversary can delay any message
  to the ledger by up to a number of
  rounds~\cite{DBLP:conf/ccs/DziembowskiFH18}, the adversary can decide to add
  no delay and thus make the communication synchronous. Therefore our result
  applies equally to such models.

  \begin{figure}[H]
    \begin{systembox}{\perfectledger}
      \begin{algorithmic}[1]
        \State State: List of txs $\mathcal{L}$
        \Statex

        \State Upon receiving (\textsc{Submit}, $m$) from \alice{} or
        \adversary, append $m$ to $\mathcal{L}$ and send (\textsc{Submit},
        \alice{} or \adversary, $m$) to \adversary
        \Statex

        \State Upon receiving (\textsc{Read}) from \alice, send (\textsc{Read},
        $\mathcal{L}$) to \alice
      \end{algorithmic}
    \end{systembox}
    \caption{}
    \label{fig:perfectledger:func}
  \end{figure}

  \begin{theorem}[Perfect Ledger is Unrealisable]
    \label{theorem:perfectledger}
    For any ITM \perfectprot{} there exist ITMs \perfectenv,
    \perfectadv{} such that for any ITM \simulator
    \begin{equation*}
      \textsc{Exec}^{\FnetworkEd^1, \gFclock}_{\perfectprot, \adversary,
      \environment} \not\approx \textsc{Exec}^{\perfectledger,
      \gFclock}_{\simulator, \environment}
    \end{equation*}
  \end{theorem}

  \begin{proofsketch}
    We take advantage of \adversary's ability to selectively send messages to
    specific players. In particular, \environment{} starts an execution with two
    players and generates a random message $m$. In half of the executions
    (randomly selected),  the adversary simulates a ``broken''  \perfectprot{}
    execution where the effects of submitting $m$ are only shared with one of
    the two players, say \alice{} by \adversary{} (in the real world). The
    environment then sends \textsc{read} to the other player, say \bob. If
    \bob{} returns a ledger containing $m$, then \environment{} concludes that
    it is the ideal world, otherwise it sends \textsc{read} to \alice. If she
    returns a ledger with $m$, then \environment{} concludes it is in the real
    world, otherwise it concludes it is in the ideal world.

    The above is not sufficient since a protocol may choose to return an empty
    ledger; to counter this, in the other half of the executions, \environment{}
    sends (\textsc{submit}, $m$) to \alice{} and then (\textsc{read}) to \bob.
    If, and only if, \bob{} knows $m$, then \environment{} concludes this is the
    ideal world. This forces the \perfectprot{} protocol to achieve instant
    finality and will establish that a distinguishing advantage exists no matter
    how \perfectprot{} is implemented.
  \end{proofsketch}

  The full proof can be found in Appendix~\ref{sec:perfect-ledger:proof}.
