\section{Preliminaries}
\label{sec:preliminaries}
  In this section we give an overview of the tools and frameworks
  used in this work.

  \subsection{Universal Composability framework}
    In simulation-based security, cryptographic tasks are defined via an ideal
    ``functionality'' $\mathcal{F}$, which can be thought of as an uncorruptible
    entity that gets the inputs of all parties and returns the expected outputs
    while also interacting with the adversary in a prescribed manner. In this
    way, the functionality expresses the essence of a cryptographic task and its
    security features. A protocol $\Pi$ realises the functionality $\mathcal{F}$
    if for any  real world adversary we can define a ``simulator'' \simulator{},
    acting as an ideal world adversary, such that any environment
    \environment{} cannot distinguish between the real world and the
    ideal world executions. Albeit a powerful tool, simulation-based security
    only works when a single instance of the protocol is run in isolation.
    However, real-world systems almost always run several programs concurrently,
    which furthermore may run different instances of the same protocol. To
    facilitate this, the Universal Composability~\cite{uc} framework
    allows us to analyse a single instance of the protocol and then
    take advantage of a generic composition theorem to infer the security of the
    protocol more broadly. This is achieved by allowing arbitrary interactions
    between the environment and the real-world adversary.

    As mentioned, lightning network members have to periodically check
    the blockchain to ensure the security of their funds. However, the execution
    model of the UC framework allows \environment{} to impose extended periods
    of inactivity to any party. We opted to avoid the complication of using the
    clock functionality to force regular activation. Restricting the analysis
    only to environments that always cater for the needed activations would
    preclude the composability of our model. We instead allow \environment{} to
    deny activation to players (therefore becoming negligent) and provide
    security guarantees conditional on \environment{} permitting the necessary
    monitoring of the blockchain.

%In particular it
%    replaces $\mathcal{F}$, $\Pi$, \adversary{}, \simulator{} and the external
%    observer with Interactive Turing Machines (ITMs). The external observer is
%    now called ``environment'' \environment{} and can interactively communicate
%    with $\Pi$ or $\mathcal{F}$, as opposed to simply providing inputs and
%    expecting outputs. \environment{} is allowed to act arbitrarily, thus
%    encapsulating anything that may happen in the system in parallel with the
%    protocol. The central result in UC allows us to prove that $\Pi$
%    ``UC-realizes'' $\mathcal{F}$, which is enough to ensure that security holds
%    no matter what \environment{} executes. More importantly, $\Pi$ may
%    internally use another functionality $\mathcal{G}$ (called a ``hybrid''). If
%    protocol $\Pi'$ has been proven to UC-realize $\mathcal{G}$, then the
%    Universal Composition theorem guarantees that \environment{} cannot
%    distinguish between an interaction with $\Pi$ using $\Pi'$ and one with
%    $\Pi$ using $\mathcal{G}$. We thus avoid proving again the security of
%    $\Pi'$ in the context of $\Pi$. Put differently, we have the power to
%    compose protocols. In this work we choose to use the UC framework in order
%    to leverage previous results on the security of blockchains.

  \subsection{Hybrid functionalities used}
    Both our main protocol $\Pi_{\mathrm{LN}}$ and the corresponding
    functionality $\fpaynet{}$ use
    \ledger~\cite{BMTZ17,genesis} as a hybrid. \ledger{} formalizes an ideal
    distributed append-only data structure akin to a blockchain. Any
    participating party can read from \ledger, which returns an ordered list
    of transactions. Furthermore parties can submit new transactions which, if
    valid, will be added to the ledger and made visible to all parties
    at the discretion of the adversary, but necessarily within a predefined time
    window. This property is called liveness. Once a transaction is added to the
    ledger, it becomes visible to all parties at the discretion of the
    adversary, but within another predefined time window, and cannot be removed
    or reordered. This is called persistence. This property arises from the
    specification of \ledger, found below. The current work makes
    heavy use of these two security properties, as the security of the lightning
    network relies crucially on the security of the underlying ledger.

    Furthermore, \ledger{} needs the \Fclock functionality,
    which models the notion of time. Every participating party can request to
    read the current time (which is initialized to 0) and inform \Fclock that
    her round is over. \Fclock increments the time by one once all parties have
    declared the end of their round.

    As already mentioned, the protocol and functionality defined in the current
    work do not make direct use of \Fclock. Indeed, the only notion of time both
    in the lightning protocol and in our work is provided by the height of the
    blockchain, as reported respectively by the underlying Bitcoin node and
    \ledger. We therefore omit it in the statement of
    Theorem~\ref{theorem:simulation} for simplicity of notation; it should
    normally appear as hybrid along with \ledger. Its exact definition can be
    found below. We also note that
    \ledger{} and \Fclock are global functionalities~\cite{globaluc} and
    therefore can be accessed directly by the environment, whereas \fpaynet{} is
    not.

  We next provide the complete description of the ledger functionality as well as the clock and network functionalities  that are
drawn from the   UC formalisation of~\cite{BMTZ17,genesis}.

  The key characteristics of the functionality are as follows. The variable
  \state maintains the current immutable state of the ledger. An honest,
  synchronised party considers finalised a prefix of \state (specified by a
  pointer position $\pt_{i}$ for party $\stkh_i$ below). The functionality has a
  parameter \windowSize such that no finalised prefix of any player will be
  shorter than $|\state| - \windowSize$. On any input originating from an honest
  party the functionality will run the \LFextend function that ensures that a
  suitable sequence of transactions will be ``blockified'' and added to \state.
  Honest parties may also find themselves in a desynchronised state: this is
  when honest parties lose access to some of their resources. The resources that
  are necessary for proper ledger maintenance and that the functionality keeps
  track of are the global random oracle \Foracle and the clock \Fclock. If an honest party maintains registration with all the resources
  then after \vdelay clock ticks it necessarily becomes synchronised.

  The progress of the \state variable is guaranteed via the \LFextend function
  that is executed when honest parties submit inputs to the functionality. While
  we do not specify \LFextend in our paper (we refer to the citations above for
  the full specification) it is sufficient to note that \LFextend guarantees the
  following properties:
  \begin{enumerate}
    \item in a period of time equal to \maxTime, a number of blocks at least
    \windowSize are
    added to \state.
    \item in a period of time equal to $\minTime$, no more blocks may be added to $\state$ if $\windowSize$ blocks have been already added. 
    \item each window of \windowSize blocks has at most \advBlocksinWindowSize\/
    adversarial blocks included in it.
    \item any transaction that (i) is submitted by an honest party earlier than
    $\frac{\vdelay}{2}$ rounds before the time that the block that is
    \windowSize positions before the head of the \state was included, 
    and (ii) is valid with respect to an honest block that extends $\state$,
    then it must be included in such block. 
  \end{enumerate}

  Given a synchronised honest party, we say that a transaction \tx is
  finalised when it becomes a part of \state in its view.

  \begin{proposition}
    \label{prop:tochain}
    Consider a synchronised honest party that submits a transaction \tx to the
    ledger functionality by the time the block indexed by $h$ is added to
    $\state$ in its view. Then \tx is guaranteed to be included in the block
    range $[h+1, h + (2 + r) \windowSize]$, where $r = \lceil (\maxTime +
    \frac{\vdelay}{2})/ \minTime \rceil$.
  \end{proposition}

  \begin{proof}
    Consider $\tau^{\stkh}_h$ to be the round that a party $\stkh$  becomes
    aware of the $h$-th block in the $\state$. It follows that $\tau_h \leq
    \tau^{\stkh}_h$ where $\tau_h$ is the round block $h$ enters $\state$. Note
    that by time $\tau_h + \maxTime$ another $\windowSize$ blocks are added to
    $\state$ and thus $\tau^{\stkh}_h \leq \tau_h + \maxTime$.

    Suppose $\stkh$ submits the transaction $\tx$ to the ledger at time
    $\tau^{\stkh}_h$. Observe that as long as $\tau_h + \maxTime$ is $\vdelay/2$
    before the time that block with index $h + t - 2\windowSize$ enters
    $\state$, then $\tx$ is guaranteed to enter the $\state$ in a block with
    index up to $h + t$ where since $\advBlocksinWindowSize < \windowSize$. It
    follows we need $\tau_h + \maxTime < \tau_{h + t - 2\windowSize} -
    \frac{\vdelay}{2}$. Let $r = \lceil (\maxTime + \frac{\vdelay}{2})/ \minTime
    \rceil$. Recall that in a period of $\minTime$ rounds at most $\windowSize$
    blocks enter $\state$. As a result $r \cdot \windowSize$ blocks require at
    least $r \cdot \minTime \geq \maxTime + \frac{\vdelay}{2}$ rounds. We deduce
    that if $t \geq (2 + r)\windowSize$ the inequality follows.
  \end{proof}

  \begin{systembox}{$\Fledger$}\vspace{1ex}
    \small
    {\bf General:}
    The functionality is parameterized by four algorithms, \LFvalidate,
    \LFextend, \LFblockify, and \vsync, along with three parameters:
    $\windowSize, \vdelay\in\mathbb{N}$, and $\StakeHolderSet :=
    \{(\stkh_{1},\stake_{1}),\ldots,(\stkh_{n},\stake_{n})\}$.
    %
    The functionality manages variables $\state$ (the immutable state of the
    ledger), $\cbuffer$ (a list of transaction identifiers to be added to the
    ledger), \buffer (the set of pending transactions), $\LFtau$ (the rules
    under which the state is extended), and \tlast (the time sequence where all
    immutable blocks where added). The variables are initialized as follows:
    $\state:=\tlast:= \cbuffer:= \varepsilon$, $\buffer:=\emptyset$, $\LFtau=0$.
  %
    For each party $\party\in\PS$ the functionality maintains a pointer $\pt_i$
    (initially set to 1) and a current-state view $\state_p:=\varepsilon$
    (initially set to empty). The functionality also keeps track of the  timed
    honest-input sequence in a vector $\TIH$ (initially $\TIH:=\varepsilon$).
    \medskip

    {\bf Party Management:}
    The functionality maintains the set of registered parties $\PS$, the
    (sub-)set of honest parties $\HO \subseteq \PS$, and the (sub-set) of
    de-synchronized honest parties $\DSyncPS\subset\HO$ (as discussed below).
    The sets $\PS, \HS, \DSyncPS$ are all initially set to $\emptyset$. When a
    (currently unregistered) honest party is registered at the ledger, {\em if
    it is registered with the clock and the global RO already,} then it is added
    to the party sets $\HS$ and $\PS$ and the current time of registration is
    also recorded; if the current time is $\LFtau > 0$, it is also added to
    $\DSyncPS$. Similarly, when a party is deregistered, it is removed from both
    $\PS$ (and therefore also from $\DSyncPS$ or $\HS$). The ledger maintains
    the invariant that it is registered (as a functionality) to the clock
    whenever $\HS \neq \emptyset$.

    \medskip

    {\bf Handling initial stakeholders:}
    If during round $\tau = 0$, the ledger did not received a registration from
    each initial stakeholder, i.e., $\party \in \StakeHolderSet$, the
    functionality halts.

    \medskip
    \hrule
    \medskip

    %\emph{To be executed upon any activation:}
    {\bf Upon receiving any input $I$} from any party or from the adversary,
    send $(\ClockRead, \sidClock)$ to \Fclock and upon receiving response
    $(\ClockRead, \sidClock, \current)$ set $\LFtau:=\current$ and do the
    following if $\current > 0$ (otherwise, ignore input):

    \begin{enumerate}\setlength\itemsep{1.5ex}
      \item Updating synchronized/desynchronized party set:
      \begin{enumerate}
        \item Let $\hat{\PS}\subseteq\DSyncPS$  denote the set of desynchronized
        honest parties that have been registered (continuously) to the ledger,
        the clock, and the GRO since time $\tau' < \LFtau-\vdelay$. Set
        $\DSyncPS:=\DSyncPS\setminus\hat{\PS}$.
        \item For any synchronized party $\party\in\HO\setminus\DSyncPS$, if
        $\party$ is not registered to the clock, then consider it
        desynchronized, i.e., set $\DSyncPS\cup\{\party\}$.
      \end{enumerate}
      \item If $I$ was received from an honest party $\party\in\PS$:\\[1ex]
      \begin{enumerate}\setlength\itemsep{1ex}
        \item Set $\TIH:=\TIH||(I,\party,\LFtau)$;
        \item Compute
        $\vec{N}=(\vec{N}_1,\ldots,\vec{N}_\ell):=\LFextend(\TIH,\state,\cbuffer,\buffer,\tlast)$
        and if $\vec{N}\neq\varepsilon$ set
        $\state:=\state||\LFblockify(\vec{N}_1)||\ldots||\LFblockify(\vec{N}_\ell)$
        and $ \tlast:=\tlast||\LFtau^\ell$, where
        $\LFtau^\ell=\LFtau||\ldots,||\LFtau$.
        \item For each $\BTX\in\buffer$: if $\LFvalidate(\BTX,\state,\buffer)=0$
        then delete  $\BTX$ from $\buffer$. Also, reset $\cbuffer:=
        \varepsilon$.
        \item If there exists $\stkh_{j}\in\HS\setminus\DSyncPS$ such that
        $|\state| -\pt_{j} > \windowSize$ or $\pt_{j} < |\state_{j}|$, then set
        $\pt_{k}:=|\state|$ for all $\stkh_{k}\in\HS\setminus\DSyncPS$.
      \end{enumerate}

      \item If the calling party $\party$ is \emph{stalled or time-unaware}
      (according to the defined party classification), then no further actions
      are taken. Otherwise, depending on the above input $I$ and its sender's
      ID, $\Fledger$ executes the corresponding code from the following list:
      \begin{itemize}
        \let\labelitemi\labelitemii
        \item \emph{Submitting a transaction:}\\
        If $I=(\LFsubmit, \sid,\tx)$ and is received from a party $\party \in
        \PS$ or from \Adv (on behalf of a corrupted party $\party$) do the
        following%\\[0.5ex]
        \begin{enumerate}\setlength\itemsep{1ex}
          \item Choose a unique transaction ID $\txid$ and set
          $\BTX:=(\tx,\txid,\LFtau,\party)$
          \item If $\LFvalidate(\BTX,\state,\buffer)=1$, then
          $\buffer:=\buffer\cup\{\BTX\}$.
          \item Send $(\LFsubmit, \BTX)$ to \Adv.%\\[2ex]
        \end{enumerate}

        \item \emph{Reading the state:}\\ If $I=(\LFread, \sid)$ is received
        from a party $\party \in \PS$ then set $\state_p:=
        \state|_{\min\{\pt_p,|\state|\}}$ and return $(\LFread, \sid, \state_p)$
        to the requester. If the requester is \Adv then send
        $(\state,\buffer,\TIH)$ to~\Adv.%\\[2ex]

        \item \emph{Maintaining the ledger state:}\\
        If $I=(\LFmine,\sid, \minerID)$ is received by an honest party
        $\party\in\PS$ and  (after updating \TIH  as above)
        $\vsync(\TIH)=\hat{\tau}>\LFtau$ then send $(\ClockUp, \sidClock)$ to
        \Fclock. Else send $I$ to \Adv.%\\[2ex]


        \item \emph{The adversary proposing the next block:} \\
        If $I=(\LFmkcore, \honestyFlag, (\txid_1,\ldots,\txid_\ell))$ is sent
        from the adversary, update \cbuffer as follows:%\\[1ex]
        \begin{enumerate}\setlength\itemsep{1ex}
          \item Set $\mathrm{listOfTxid} \gets \epsilon$
          \item For $i=1,\ldots, \ell$ do: if there exists
          $\BTX:=(x,\txid,\minerID,\LFtau,\stkh_j)\in\buffer$ with ID
          $\txid=\txid_i$ then set
          $\mathrm{listOfTxid}:=\mathrm{listOfTxid}||\txid_i$.
          \item Finally, set $\cbuffer:= \cbuffer
          ||(\honestyFlag,\mathrm{listOfTxid})$ and output $(\LFmkcore, ok)$ to
          \Adv.%\\[2ex]
        \end{enumerate}
        \item \emph{The adversary setting state-slackness:}\\
        If $I=(\LFslack,(\stkh_{i_1},\hat{\pt}_{i_1}),\ldots,
        (\stkh_{i_\ell},\hat{\pt}_{i_\ell})),$ with
        $\{\party_{i_1},\ldots,\party_{i_\ell}\}\subseteq\HS\setminus\DSyncPS$
        is received from the adversary \Adv do the following:%\\[1ex]
        \begin{enumerate}\setlength\itemsep{1ex}
          \item If for all $j\in[\ell]:$  $|\state|
          -\hat{\pt}_{i_j}\leq\windowSize$ and $\hat{\pt}_{i_j}\geq
          |\state_{i_j}|$, set $\pt_{i_1}:=\hat{\pt}_{i_1}$ for every
          $j\in[\ell]$ and return $(\LFslack,ok)$ to \Adv.
          \item Otherwise set $\pt_{i_j}:=|\state|$ for all $j\in[\ell]$.
        \end{enumerate}
        \item \emph{The adversary setting the state for desychronized
        parties:}\\
        If $I=(\LFdsstate,(\stkh_{i_1},\state_{i_1}'),\ldots,
        (\stkh_{i_\ell},\state_{i_\ell}')),$ with
        $\{\stkh_{i_1},\ldots,\stkh_{i_\ell}\}\subseteq\DSyncPS$ is received
        from the adversary \Adv, set $\state_{i_j}:=\state_{i_j}'$ for each
        $j\in[\ell]$ and return $(\LFdsstate,ok)$ to \Adv.
      \end{itemize}
    \end{enumerate}
  \end{systembox}


  \ignore{ %%% WE SKIP THE BELOW FOR SIMPLICITY
  \subsection{Formal Specification of \LFextend for the PoS Ledger}\label{app:model_extpol}

  The detailed ExtendPolicy for Ouroboros is given below. % for completeness.
  %The extend policy is
  %parameterized by the ledger parameters that control the speed and the quality of
  %the ledger.

  \begin{algobox}{\LFextend for $\Fledger$}
    \begin{algorithmic}
      \Function{\text{$\LFextend$}}{$\TIH,\state,\cbuffer,\buffer,\tlast$}
    \State \Comment{First, create a default honest client block as alternative:}  
      \State $\defaultblock \gets$ \Call{DefaultExtension}{$\TIH,\LFstate,\cbuffer,\buffer,\tlast$} \Comment{Extension if adversary violates policy.}
      \State Let $\tau_L$ be current ledger time (computed from $\TIH$)  
      \State \Comment{The function must not have side-effects: Only modify copies of relevant values.}
      \State Create local copies of the values $\buffer$, $\state$, and $\tlast$.
    
      \State \Comment{Now, parse the proposed block by the adversary}
      \State Parse $\cbuffer$ as a vector $((\honestyFlag_1,\cbuffer_1), \cdots, (\honestyFlag_n, \cbuffer_n))$
      \State $\vec{N} \gets \varepsilon$
      \quad\Comment{Initialize Result}
      \State \Comment{Determine the time of the state block which is $\windowSize$ blocks behind the head of the state}
      \If{$|\state| \geq \windowSize$}
      \State Set $\timeLast \gets \tlast[|\state|-\windowSize + 1]$
      \Else
      \State Set  $\timeLast \gets 1$
      \EndIf
      \State $\mathsf{oldValidTxMissing} \gets \mathsf{false}$ \quad \Comment{Flag to keep track whether old enough, valid transactions are inserted.}
      \For{each list $\cbuffer_i$ of transaction IDs}  
      \State \Comment{Compute the next state block}
      \State \Comment{Verify validity of $\cbuffer_i$ and compute content}
      \State Use the $\txid$ contained in $\cbuffer_i$ to determine the list of transactions
      \State Let $\vec{\tx}=(\tx_1,\dots,\tx_{|\cbuffer_i|})$ denote the transactions of $\cbuffer_i$
      \If{$\tx_1$ is not a coin-base transaction}
      \State \Return $\defaultblock$
      \Else
      \State $\vec{N}_i \gets \tx_1$
      \For{$j=2$ to $|\cbuffer_i|$}
      \State Set $\st_i \gets \bitcoinBlockify(\vec{N}_i)$
      \If{$\bitcoinValid(\tx_j,\state||\st_i)=0$}
      \State  \Return $\defaultblock$
      \EndIf
      \State $\vec{N}_i \gets \vec{N}_i||\tx_j$
      \EndFor
      \State Set $\st_i \gets \bitcoinBlockify(\vec{N}_i)$
      \EndIf
      
      \State \Comment{Test that all old valid transaction are included}
      \If{the proposal is declared to be an honest block, i.e., $\honestyFlag_i=1$}
      \For{each $\BTX=(\tx,\txid,\tau',\party) \in \buffer$ of an honest party $\party$ with time $\tau' < \timeLast - \frac{\vdelay}{2}$}
      \If{$\bitcoinValid(\tx,\state||\st_i)=1$ but $\tx \not \in \vec{N}_i$}
      \State $\mathsf{oldValidTxMissing} \gets \mathsf{true}$
      \EndIf
      \EndFor
      \EndIf
      \State $\vec{N} \gets \vec{N}||\vec{N}_i$
      \State $\state \gets \state||\st_i$
      \State $\tlast \gets \tlast||\tau_L$
      \State \Comment{Must not proceed with too many adversarial blocks}
      \State $i \gets \max\lbrace \{\windowSize\} \cup \{k \ | \ \st_k \in \state \wedge \, \text{proposal of } \st_k \text{ had } \honestyFlag=1\}\rbrace$ \Comment{Determine most}
      \State \Comment{recent honestly-generated block in the interval behind the head.}
      \If{$|\state|-i \geq \advBlocksinWindowSize$}
      \State \Return $\defaultblock$
      \EndIf
      
      \State \Comment{Update $\timeLast$: the time of the state block which is $\windowSize$ blocks behind the head of the}
      \State \Comment{current, potentially already extended state}
      \If{$|\state| \geq \windowSize$}
      \State Set $\timeLast \gets \tlast[|\state|-\windowSize + 1]$
      \Else
      \State Set  $\timeLast \gets 1$
      \EndIf
      \EndFor
      
      %Now, the checks proceed.
      \State \Comment{Final checks (if policy is violated, it is enforced by the ledger):}
      \State \Comment{Must not proceed too slow or with missing transaction.}
      \If{$\timeLast > 0$ \textbf{and}  $\tau_L - \timeLast > \maxTime$} \Comment{A sequence of blocks cannot take too much time.}
      \State \Return $\defaultblock$
      \ElsIf{$\timeLast = 0$ \textbf{and}  $\tau_L - \timeLast > 2\cdot\maxTime$} \Comment{Bootstrapping cannot take too much time.}
      \State \Return $\defaultblock$
      \ElsIf{$\mathsf{oldValidTxMissing}$} \Comment{If not all old enough, valid transactions have been included.}
      \State \Return $\defaultblock$
      \EndIf
      \State \Return $\vec{N}$
      \EndFunction
    \end{algorithmic}
  \end{algobox}



  \begin{figure}
  \begin{algobox}{{\bf for Default State Extension}}
    \begin{algorithmic}
      \Function{{DefaultExtension}}{$\TIH,\LFstate,\cbuffer,\buffer,\tlast$}
      \State {\it \textcolor{gray}{We assume call-by-value and hence the function has no side effects.}}
      \State {\it \textcolor{gray}{The function returns a policy-compliant extension of the ledger state.}}
      \State
      \State Set $\defaultblock\gets \coinbase{\minerID}$ of an honest
      miner
      \State Sort $\buffer$ according to time stamps.
      \State Let $\vec{\tx}=(\tx_1,\dots,\tx_{\ell})$ be the transactions in $\buffer$
      \State Set $\st \gets \bitcoinBlockify(\defaultblock)$
      \Repeat
      \State Let $\vec{\tx}=(\tx_1,\dots,\tx_{\ell})$ be the current list of (remaining) transactions
      \For{$i=1$ to $\ell$}
      \If{$\bitcoinValid(\tx_i,\state||\st)=1$}
      \State $\defaultblock \gets \defaultblock||\tx_i$
      \State Remove $\tx_i$ from $\vec{\tx}$
      \State Set $\st \gets \bitcoinBlockify(\defaultblock)$
      \EndIf
      \EndFor
      \Until{$\defaultblock$ does not increase anymore}  
      %PG: I guess this is a forgotten comment from an older version?
      %\State \Comment{Possibly more than one block have to be added}
      \State \Comment{Let $\timeLast$ be the time of the block which is $\windowSize-1$ blocks behind the head of the state.}
      \If{$|\state| + 1 \geq \windowSize$}
      \State Set $\timeLast \gets \tlast[|\state|-\windowSize + 2]$
      \Else
      \State Set  $\timeLast \gets 1$ \Comment{First epoch starts at time $1$ (time $0$ is initialization time).}
      \EndIf
      \State $c \gets 1$
      \While{$\tau_L - \timeLast > \maxTime$}
      \State Set $\vec{N}_c \gets \coinbase{\minerID}$ of an honest miner
      \State $\defaultblock \gets \defaultblock||\vec{N}_c$
      \State $c \gets c+1$
      \State \Comment{Update $\timeLast$ to the time of the state block which is $\windowSize-c$ blocks behind the head.}
      \If{$|\state| + c \geq \windowSize$}
      \State Set $\timeLast \gets \tlast[|\state|-\windowSize + c + 1]$
      \Else
      \State Set  $\timeLast \gets 1$
      \EndIf
      \EndWhile  
      \State \Return $\defaultblock$
      \EndFunction
    \end{algorithmic}
  \end{algobox}
  \caption{Function to compute a policiy-compliant default ledger-state extension.}
  \label{fig:defaultExtension}
  \end{figure}
  }%%%%%%%%%%%


  \begin{systembox}{Functionality $\Fclock$}
    The functionality manages the set $\PS$ of registered identities, i.e.,
    parties $\party = (\pid,\sid)$. It also manages the set $F$ of
    functionalities (together with their session identifier). Initially,
    $\PS:=\emptyset$ and $F := \emptyset$.

    \smallskip
    For each session $\sid$ the clock maintains a variable $\current_\sid$. For
    each identity $\party := (\pid,\sid) \in \PS$ it manages variable
    $d_\party$. For each pair $(\Func,\sid) \in F$ it manages variable
    $d_{(\Func,\sid)}$ (all integer variables are initially $0$).

    \medskip

    \emph{Synchronization:}
    \begin{itemize}
      \item Upon receiving $(\ClockUp, \sidClock)$ from some party $\party \in
      \PS$ set $d_{\party}:=1$; execute \emph{Round-Update} and forward
      $(\ClockUp, \sidClock, \party)$  to $\Adv$.

      \item Upon receiving $(\ClockUp, \sidClock)$ from some functionality
      $\Func$ in a session $\sid$ such that $(\Func,\sid) \in F$ set
      $d_{(\Func,\sid)}:=1$, execute \emph{Round-Update} and return $(\ClockUp,
      \sidClock,\Func)$ to this instance of $\Func$.

      \item Upon receiving $(\ClockRead, \sidClock)$ from any participant
      (including the environment on behalf of a party, the adversary, or any
      ideal---shared or local---functionality) return $(\ClockRead,
      \sid,\current_\sid)$ to the requestor (where $\sid$ is the sid of the
      calling instance).
    \end{itemize}

    \emph{Procedure Round-Update:}
    For each session $\sid$ do:
    If $d_{(\Func,\sid)}:=1$ for all $\Func \in F$ and $d_{\party}=1$ for all
    honest parties $\party=(\cdot,\sid) \in \PS$, then set
    $\current_\sid:=\current_\sid+1$  and reset $d_{(\Func,\sid)}:=0$ and
    $d_{\party}:=0$ for all parties $\party=(\cdot,\sid) \in \PS$.
  \end{systembox}

  \subsection{Transaction structure}
    \ledger{} does not define what is a valid transaction, but leaves it as a
    system parameter. Importantly, no notion of coins is built in \ledger. We
    therefore specify a valid transaction, closely following concepts put forth
    in Bitcoin~\cite{bitcoin}, but avoiding specifying the entire Bitcoin
    script.

    At a high level, every transaction consists of inputs and outputs. Each
    output has an associated value in coins and a number of ``spending
    methods''. A spending method specifies the exact requirements for spending
    the output. Each input must be connected to exactly one output and satisfy
    one of its spending methods.

    Transactions in \ledger{} form a DAG. A new transaction is valid only if
    each of its inputs correctly spends an output with no other connected input
    and the sum of the values of its outputs does not exceed the sum of the
    values of the outputs connected to its inputs. We refer the reader to
    Section~\ref{appendix:txstructure} for a complete overview.

  \subsection{Cryptographic Primitives}
    In the Lightning Network specification, a custom scheme for deriving keys is
    used. Its syntax and security aims closely match those of previously studied
    Identity Based Signature schemes~\cite{ibsshamir,ibspaterson}, thus we use
    the latter to abstract away the complexity of the construction and highlight
    the security requirements it satisfies. We slightly modify previous IBS
    schemes by adding an algorithm that, on input of the public parameters $mpk$
    and a label $l$, returns the verification key $pk_l$. Such an IBS scheme
    provides 5 algorithms:
    \begin{itemize}
      \item $(mpk, msk) \leftarrow \textsc{Setup}(1^k)$: master keypair
      generation
      \item $(pk_l, sk_l) \leftarrow \textsc{KeyDer}(mpk, msk, l)$: keypair
      derivation with label $l$
      \item $pk_l \leftarrow \textsc{PubKeyDer}(mpk, l)$: verification key
      derivation with label $l$
      \item $\sigma \leftarrow \textsc{SignIBS}(m, sk_l)$: signature generation
      with signing key $sk_l$
      \item $\{0, 1\} \leftarrow \textsc{VerifyIBS}(\sigma, m, pk_l)$: signature
      verification
    \end{itemize}
    We refer the reader to~\cite{ibspaterson} and to Section~\ref{sec:ibs} for more details. Other
    cryptographic primitives used are digital signatures (Section~\ref{sec:ds}) and pseudorandom
    functions (Section~\ref{sec:prf}). Finally, a less common two-party cryptographic primitive is
    employed that we formalise as \emph{combined digital signatures}, see
    Section~\ref{sec:ov-combined-ds}.
