\begin{systembox}{$\fpaynet{}_{\mathrm{, dummy}}$}
  \label{alg:fpaynet:dummy}
  \begin{algorithmic}[1]
    \State Upon receiving any message $M$ from \alice: send ($M, \alice$) to
    \simulator
    \State Upon receiving any message ($M, \alice$) from \simulator: send $M$ to
    \alice
  \end{algorithmic}
\end{systembox}

\begin{simulatorbox}{$\simulator{}_{\mathrm{LN}}$}
  \label{alg:sim:ln}
  Expects the same messages as the protocol, but messages that the protocol
  expects to receive from \environment, the simulator expects to receive from
  $\fpaynet{}_{\mathrm{, dummy}}$ with the name of the player appended. The
  simulator internally executes one copy of the protocol per player. Upon
  receiving any message, the simulator runs the relevant code of the protocol
  copy tied to the appended player name. Mimicking the real-world case, if a
  protocol copy sends a message to another player, that message is passed to
  \adversary{} as if sent by the player and if \adversary{} allows the message
  to reach the receiver, then the simulator reacts by acting upon the message
  with the protocol copy corresponding to the recipient player. A message sent
  by a protocol copy to \environment{} will be routed by \simulator{} to
  $\fpaynet{}_{\mathrm{, dummy}}$ instead. To distinguish which player it comes
  from, \simulator{} also appends the player name to the message.
\end{simulatorbox}

\begin{lemma}
  \label{lemma:dummy}
  $\textsc{Exec}^{\ledger}_{\Pi_{\mathrm{LN}}, \adversary_{\mathrm{d}},
  \environment} = \textsc{Exec}^{\fpaynet{}_{\mathrm{, dummy}},
  \ledger}_{\simulator_{\mathrm{LN}}, \environment}$
\end{lemma}
\begin{proof}
  Consider a message that \environment{} sends. In the real world, the protocol
  ITIs produce an output. In the ideal world, the message is given to
  $\simulator{}_{\mathrm{LN}}$ through $\fpaynet{}_{\mathrm{, dummy}}$. The
  former simulates the protocol ITIs of the real world (along with their coin
  flips) and so produces an output from the exact same distribution, which is
  given to \environment{} through $\fpaynet{}_{\mathrm{, dummy}}$. Thus the two
  outputs are indistinguishable.
\end{proof}
