\section{Transaction Structure}
  \label{appendix:txstructure}
  A well-formed transaction consists of a list of inputs and a list of outputs.
  For the transaction to be valid, each input must be connected to a single
  valid, previously unconnected (unspent) output of another transaction in
  \ledger.

  A well-formed output consists of a value in coins and a list of ``spending
  methods''. A well-formed input consists of a reference to a previously
  unconnected output and a reference to a single of the latter's spending
  methods, along with the data needed to satisfy that method. A well-formed
  spending method contains any combination of the following:
  \begin{itemize}
    \item Public keys in disjunctive normal form. An input that spends using
    this spending method must contain signatures valid by the public keys of one
    of the conjunctions. If no public keys are specified in the output, no
    signatures are needed in the input.
    \item Absolute locktime $d_a$, in block height or time. An input that spends
    this output can only be in block of height at least $d_a$ if $d_a$ is a
    block height, or enter the ledger on or after time $d_a$ otherwise. Zero
    means no absolute locktime.
    \item Relative locktime $d_r$, in block height or time. The distance of an
    input that spends this output must be at least $d_r$, counted in block
    height or time. Zero means no relative locktime.
    \item Hashlock value. The output can be spent by an input that contains a
    preimage that hashes to the hashlock value. If no hashlock value is
    specified in the output, no preimage is needed in the spending input.
  \end{itemize}

  Lastly, the sum of coins of the outputs referenced by the inputs of the
  transaction (to-be-spent outputs) should be greater than or equal to the sum
  of coins of the outputs of the transaction.

  We say that an unspent output is currently exclusively spendable by a player
  $Alice$ with a public key $pk$ and a hash list $hl$ if for each spending
  method one of the following two holds:
  \begin{itemize}
    \item It still has a locktime that has not expired and thus is currently
    unspendable, or
    \item The only specified public key is $pk$ and if there is a hashlock, its
    hash is contained in $hl$.
  \end{itemize}
  If an output is exclusively spendable, we say that its coins are exclusively
  spendable.
